\fontfamily{phv}\selectfont{Causal Discovery methods for Effective Connectivity}

### 2013-09-27 docs/proposal/doc.tex
abstract toegevoegd

\begin{abstract}
Lorem Ipsum Dolor Sit Amet.
\keywords{Keywords}
\end{abstract}

@@

Another causal discovery method is the BCCD-algorithm \cite{claassen2012}, which gives similar results as PC, and is designed in an attempt to improve PC.
This algorithm has some useful properties; it is a Bayesian approach and as such, it is more robust against noise.
The authors have shown the method to perform as good as or better than other causal discovery algorithms such as PC on representative datasets.
As is inherent to Bayesian methods, or approximations of Bayesian methods, the resulting network graph is not a  single structure but rather a distribution over possible structures.
Concretely, this provides an uncertainty measure over edges in the network, giving additional information compared to PC.

>>>>

\begin{abstract}
In the field of brain research, different forms of connectivity are considered. To find effective connectivity, many different approaches have been used. In this project, we will apply causal discovery the methods of PC and BCCD to structural and functional connectivity, to infer effective connectivity. As data from multiple subjects will be used, evaluation of the result can show whether the method yields consistent results.
\keywords{Keywords}
\end{abstract}

@@

Another causal discovery method is the Baysian Constraint-based Causal Discovery (BCCD) algorithm \cite{claassen2012}, which gives similar results as PC, and is designed in an attempt to improve PC.
This algorithm has some useful properties; it is a Bayesian approach and as such, it is more robust against noise.
The authors have shown the method to perform as good as or better than other causal discovery algorithms such as PC on representative datasets.
As is inherent to Bayesian methods, or approximations of Bayesian methods, the resulting network graph is not a  single structure but rather a distribution over possible structures.
Concretely, this provides an uncertainty measure over edges in the network, giving additional information compared to PC.
